Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-09 volunteer-clouds-ieee-ci-si.tex

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{img/ips-time-ww.png}
\caption{Time employed in every experiment vs. number of IPs (in abscises). The red dot and line show the average and standard deviation, the shade of blue the number of experiments with the same number of IPs. }
\label{fig:ipstime:w2}
\end{figure}
%
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value distribution of
  the number of {\tt PUT}s per worker. \label{tab:puts:ww}}
\begin{center}
\begin{tabular}{ccc}
\hline
Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
18.275 $\pm$ 0.83719  &  25.962  $\pm$ 1.22015 & 1.242   $\pm$ 0.04746 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{img/gev-fit-ww.png}
\caption{Ranked number of {\tt PUT}s per worker and GEV fit (in red)
  for the {\sf NodIO$^2$} model. }
\label{fig:gev:w2}
\end{figure}
%
It is also interesting to measure the scaling properties in this
model, that is, the relationship between the number of IPs
participating in an experiment and the time it takes to complete
it. This is shown in Figure \ref{fig:ipstime:w2}, which shows every
experiment in a time (in milliseconds) vs. number of workers participating
in it. Although there is not a clear trend, the graph seems to say
that the time needed for finding the solution in this evolutionary
algorithm does not depend on the number of workers participating in
it. This does not mean that it is independent on the number of {\em
  simultaneous} users, which is probably the case although it is more
difficult to measure. There seems to be a trend towards a decreasing
standard deviation in the time, with more volunteers adding {\em
  robustness} to an experiment and certainty in the time it is taking;
however, more experiments would be needed to check this hypothesis.

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{img/ips-time-ww.png}
\caption{Time employed in every experiment vs. number of IPs (in abscises). The red dot and line show the average and standard deviation, the shade of blue the number of experiments with the same number of IPs. }
\label{fig:ipstime:w2}
\end{figure}
%
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value distribution of
  the number of {\tt PUT}s per worker. \label{tab:puts:ww}}
\begin{center}
\begin{tabular}{ccc}
\hline
Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
18.275 $\pm$ 0.83719  &  25.962  $\pm$ 1.22015 & 1.242   $\pm$ 0.04746 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{img/gev-fit-ww.png}
\includegraphics[width=0.49\linewidth]{img/weibull-fit-ww.png}
\caption{Ranked number of {\tt PUT}s per worker and GEV fit (in red, right) and Weibull (in red, left) for the {\sf NodIO$^2$} model. }  
\label{fig:gev:w2}
\end{figure}
%
It is also interesting to measure the scaling properties in this
model, that is, the relationship between the number of IPs
participating in an experiment and the time it takes to complete
it. This is shown in Figure \ref{fig:ipstime:w2}, which shows every
experiment in a time (in milliseconds) vs. number of workers participating
in it. Although there is not a clear trend, the graph seems to say
that the time needed for finding the solution in this evolutionary
algorithm does not depend on the number of workers participating in
it. This does not mean that it is independent on the number of {\em
  simultaneous} users, which is probably the case although it is more
difficult to measure. There seems to be a trend towards a decreasing
standard deviation in the time, with more volunteers adding {\em
  robustness} to an experiment and certainty in the time it is taking;
however, more experiments would be needed to check this hypothesis.
